\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-09-09 ResponseToReview.tex

Nevertheless, the manuscript is worth publishing as it does present data that may help rule out some possible explanations as to why tb1 is so common in parviglumus.\\

\res{Thank you; we hope that our paper in conjunction with future research and experiments can help shed light on the ecological significance of both \emph{tb1} and the \emph{Hopscotch} insertion in teosinte.}

6) This paper is fairly maize-centric. A more general message is included in the discussion, not as much in the introduction, and not at all in the abstract. This could be easily remedied.\\

\res{We have editied the introduction to include a more broad explanation of domestication and shade avoidance responses in plants. Edits can be seen on page 2, lines 22-45 and page 5, lines 70-78.}

### 2014-09-09 manuscript.tex
Edits
added URL for chunking script

We examined evidence of introgression on chromosome 1 in these same four populations (EjuA, EjuB, MSA, SLO) using STRUCTURE \citep{Falush2003} and phased data from \citet{Pyhajarvi2013}, combined with the corresponding SNP data from a diverse panel of 282 maize lines \citep{Cook2012}. SNPs were anchored in a modified version of the IBM genetic map \citep{Gerke2013}. Since STRUCTURE does not account for LD due to physical linkage we created haplotype blocks using a custom Perl script from \citet[][code available at \lev{Matt is your code available through your github?} \url{XXX}]{Hufford2013}.  In maize, LD decays over an average distance of 5500bp \citep{Chia2012}; because LD decay is even more rapid in teosinte \citep{Chia2012} we used a conservative haplotype block size of 5kb.  We ran STRUCTURE at K=2 under the linkage model, performing 3 replicates with an MCMC burn-in of 10,000 steps and 50,000 steps post burn-in.

>>>>

We examined evidence of introgression on chromosome 1 in these same four populations (EjuA, EjuB, MSA, SLO) using STRUCTURE \citep{Falush2003} and phased data from \citet{Pyhajarvi2013}, combined with the corresponding SNP data from a diverse panel of 282 maize lines \citep{Cook2012}. SNPs were anchored in a modified version of the IBM genetic map \citep{Gerke2013}. Since STRUCTURE does not account for LD due to physical linkage we created haplotype blocks using a custom Perl script from \citet[][code available at \url{http://dx.doi.org/10.6084/m9.figshare.1165577}]{Hufford2013}.  In maize, LD decays over an average distance of 5500bp \citep{Chia2012}; because LD decay is even more rapid in teosinte \citep{Chia2012} we used a conservative haplotype block size of 5kb.  We ran STRUCTURE at K=2 under the linkage model, performing 3 replicates with an MCMC burn-in of 10,000 steps and 50,000 steps post burn-in.
